---
title: "individual2"
output: html_document
---

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco)

```


1) 


```{r}
hist(choco$Rating, main = "Histogram of Chocolate Ratings")

```

```{r}
boxplot(choco$Rating, main = "Boxplot of Chocolate Ratings")

summary(choco$Rating)

```
Most of the ratings are between 2.4 and 3.9. There are no ratings between 3.0 and 3.2. There are four outliers under 2.0.


2) 

```{r}
table(choco$Date)
a <- table(choco$Date)
barplot(a, main = "Barplot of Chocolate Rating")

```

Ratings seem to be increasing everywhere up untl 2016. 2014 and 2015 have the highest years for rating count.


3) 

```{r}
plot(x = choco$Cocoa_Percent, y=choco$Rating)

summary(choco$Cocoa_Percent)


```

The datapoints are scattered without much relation between cocoa percent and rating. 


4)
```{r}
#Most common characteristics in lower rated chocolates: Rating of 3.25 or Less

sort(table(choco[choco$Rating <= 3.25, ]$Characteristics1))

  #highest is sandy: 98 

sort(table(choco[choco$Rating <= 3.25, ]$Characteristics2))

  #highest is sweet: 98

sort(table(choco[choco$Rating <= 3.25, ]$Characteristics3))

  #highest is sour: 56



```

Chocolates with sandy, sweet or sour tastes trend for ratings less than or equal to 3.25


```{r}

#Most common characteristics in higher rated chocolates: Rating between 3.5 and 4.0

sort(table(choco[choco$Rating >= 3.5, ]$Characteristics1))

  #highest is creamy: 105

sort(table(choco[choco$Rating >= 3.5, ]$Characteristics2))

  #highest is nutty: 38

sort(table(choco[choco$Rating >= 3.5, ]$Characteristics3))

  #highest is cocoa: 51

```

Chocolates that are creamy, nutty or cocoa trend with ratings between 3.5 and 4.0.

