---
title: "individual1"
author: "Seungah Lee"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

1. How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.

```{r}
hist(choco$Rating, main = "Histogram of Chocolate Rating")

```

```{r}
boxplot(choco$Rating, main = "Boxplot of Chocolate Rating")

#There are four outliers.
```




2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}

table(choco$Date)
a <- table(choco$Date)
barplot(a, main = "Barchart of Chocolate Rating")

barplot(table(choco$Date), main = "Barchart of Chocolate Rating")
```


3. Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain.
Now, we are ready to explore.

```{r}
summary(choco$Cocoa_Percent)

plot(choco$Cocoa_Percent, choco$Rating,
     main = "Scatterplot of Cocoa Percent",
     xlab = "Cocoa percent",
     ylab = "Rating")


```

     
4. How do different characteristics of the chocolate compare? To elaborate, which characteristics tend to be more favorable and which ones are not? Create both numerical and graphical summaries, and explain.

```{r}
topfavor <- choco[choco$Rating >= 4,]

topfavor5char1 <- sort(table(topfavor$Characteristics1), 
                   decreasing=TRUE)[1:5]
topfavor5char1

topfavor5char2 <- sort(table(topfavor$Characteristics2), 
                   decreasing=TRUE)[1:5]

topfavor5char2

topfavor5char3 <- sort(table(topfavor$Characteristics3), 
                   decreasing=TRUE)[1:5]

topfavor5char3

table

barplot(topfavor5char1, main = "Top favor 5")

```


5. Brainstorm two analyses you would like to perform with your teammate. Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.
